### 2022-03-07 manuscript.tex
imagesize [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e/checks
https://github.com/scherzerthesis/thesis/actions/runs/1948487610

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/cb15eaa36551642a3015ab49949d551fc56653b6/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/cb15eaa36551642a3015ab49949d551fc56653b6}{scherzerthesis/thesis@cb15eaa}
on March 7, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tubaseq_figure1.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:06}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure1_021022.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure2_021722.svg}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure3_021722.svg}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure4_021722.svg}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e}{scherzerthesis/thesis@8525232}
on March 7, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/tubaseq_figure1.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:06}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure1_021022.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure2_021722.svg}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure3_021722.svg}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure4_021722.svg}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}
